---
title: "Bootstrapping"
author:
  - name: Sajal Shrestha 
    url: https://sajalshres.github.io
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Bootstrapping can be useful to draw a valid inference when the sample size is small. We can use a resampling method with replacement to create any number of resamples. For implementing bootstrapping, I came across a useful package [boot](https://www.rdocumentation.org/packages/boot/versions/1.3-28/topics/boot) that generates bootstrap replicates of a statistics applied to data.

## Load Packages

```{r load-package}
library(tidyverse)
library(boot)
```

## Data Overview

To implement bootstrap resampling, I've used builtin `Loblolly` dataset that contains the data about the growith of the Loblolly pine tree.

```{r data-overview}
data("Loblolly", package = "datasets")
knitr::kable(head(Loblolly))
```

```{r data-summary}
summary(Loblolly)
```

```{r bootstrap-statistics-function}
# A function which when applied to data returns a vector containing the statistic(s) of interest.
statistics_function <- function(data, i){
 d2 <- data[i,] 
 return(cor(d2$height, d2$age))
}
```

In the above code, I've defined a custom function `statistics_function` that accepts two parameters, namely, `data` and `i`. The `data` parameter denotes the dataset as the name suggest where as `i` parameter is the index denoting the row of the data that will be used to create bootstrap sample.

```{r bootstrap-correlation}
set.seed(518)
bootstrap_correlation <- boot(Loblolly, statistic = statistics_function, R = 10000)
```

Now, we apply the `boot` function which accepts dataset, statistic fucntion and number of bootstrap sample. The `seed` function is used in this context to generate reproducible results.

```{r}
bootstrap_correlation
```
We can observe that the correlation between two variable is 0.989 with a standard error of 0.0016.

```{r bootstrap-correlation-overview}
summary(bootstrap_correlation)
```

Similarly, we can view the value of the `boot` object.

Below, we have generated range, mean and standard deviation of bootstrap samples.

```{r bootstrap-additional-statistics-range}
range(bootstrap_correlation$t)
```

The bootstrap correlation ranges from 0.982 to 0.995

```{r bootstrap-additional-statistics-mean}
mean(bootstrap_correlation$t)
```

The mean for bootstrap correlation is 0.989.

```{r bootstrap-additional-statistics-sd}
sd(bootstrap_correlation$t)
```

The standard deviation for boostrap correlation is 0.001.


```{r bootstrap-confidence-interval}
boot.ci(boot.out=bootstrap_correlation,type=c('norm','basic','perc','bca'))
```


The above function call `boot.ci` demonstrates the confidence interval of 4 types: normal, basic, percentile and bca distribution.