---
title: "Data Management"
author:
  - name: Sajal Shrestha 
    url: https://sajalshres.github.io
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Data

I imported the Airbnb data set for the Chicago city in to the dataframe. Below is the code to import into the dataframe.

```{r load_package, message=FALSE}
library(tidyverse)
```

```{r import-data, message=FALSE}
listings <- readr::read_csv("data/raw/chicago_listings.csv")
reviews <- readr::read_csv("data/raw/chicago_reviews.csv")
listings_missing_data <- listings
```

## Managing data

The dataset has more than 80 columns. I removed them using `dplyr::select` function. Also, some of the data were in unexpected format. I modified them using `dplyr::mutate` function.

```{r}
# Remove unwanted columns
listings <- listings %>%
  select(
    id,
    name,
    description,
    host_id,
    host_name,
    host_since,
    host_location,
    host_about,
    host_response_time,
    host_response_rate,
    host_acceptance_rate,
    host_is_superhost,
    host_neighbourhood,
    host_verifications,
    host_identity_verified,
    host_has_profile_pic,
    neighbourhood_cleansed,
    latitude,
    longitude,
    property_type,
    room_type,
    accommodates,
    bathrooms_text,
    bedrooms,
    beds,
    price
  ) %>%
  mutate(host_since = format(as.Date(host_since), "%m/%d/%Y"),
         .after = host_name) %>%
  mutate(bathrooms = parse_number(str_extract(bathrooms_text, "\\d*\\.?\\d+")), .after = beds) %>%
  mutate(price = parse_number(price),) %>%
  select(!bathrooms_text) %>%
  rename(neighbourhood = neighbourhood_cleansed)
```

## Cleaning Data

Some of the rows had empty strings or labelled with "N/A" value. I replaced them with `NA` and dropped the data for some of the columns which had `NA`.

```{r}
# Replace empty values with NA
listings[listings == ""] <- NA

# Replace N/A values with NA
listings[listings == "N/A"] <- NA

# Drop rows with NA in id, name
listings <- listings %>%
  drop_na(c("id", "name", "host_id", "host_name", "host_location", "host_neighbourhood"))
```

Also, I detected some noise in the dataset where the location was from wrong countries, city or state. I used `dplyr::filter` function to remove such noises.

```{r}
listings <- listings %>%
  filter(
    host_location == "Chicago, Illinois, United States"
  )
```



