---
title: "Functions"
author:
  - name: Sajal Shrestha 
    url: https://sajalshres.github.io
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(httr)
```


## Functions

I have also built a user defined function that is used to search the github repositories. The function `search_github_repositories` accepts three parameters:

- **query**: The search keywords.
- **sort**: Sorts the results of your query by number of stars, forks, or help-wanted-issues
- **order**: Determines whether the first search result returned is the highest number of matches (desc) or lowest number of matches (asc).

The function makes an http request using the `httr` library to the github api endpoint. Next, the status code is checked and upon success, the response is parsed.

```{r user-function-definition}
search_github_repositories <-
  function(query, sort = "stars", order = "desc") {
    # urls
    github_api_url <- "https://api.github.com"
    search_endpoint <- "/search/repositories"
    
    # build query params
    query_params <-
      paste(paste0("?q=", query),
            paste0("sort=", sort),
            paste0("order=", order),
            sep = "&")
    
    print(paste("Url is",github_api_url, search_endpoint, query_params))
    
    # make http request to Github Api
    response <-
      httr::GET(url = paste0(github_api_url, search_endpoint, query_params))
    
    response_status_code <- httr::status_code(response)
    
    # Stop if unexpected status code
    if (response_status_code != 200) {
      stop(paste0("Unexpected status", response_status_code, "encountered"))
    }
    
    # Parse the JSON response
    response_parsed <- httr::content(response, as = "parsed")
    
    # Print stats
    print(paste(
      "Search for",
      query,
      "found",
      response_parsed$total_count,
      "results"
    ))
    
    return(response_parsed)
  }
```

The below code chuck demonstrate how to call the created function.

```{r user-function-call}
# Search for repositories with name sta-518
search_response <- search_github_repositories(query = "sta-518")
search_response$items[[1]]$full_name
search_response$items[[1]]$owner$url
```

