---
title: "Graphical Visualizations and Summaries"
author:
  - name: Sajal Shrestha 
    url: https://sajalshres.github.io
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-package}
library(tidyverse)
```

For creating graphical visualizations, I've used ggplot2 library. Using the library, I've generated numerous visualizations such as bar chart(`geom_bar`), boxplots(`geom_boxplot`), histogram(`geom_histogram`), scatter plots(`geom_point`).


```{r visual-missing-values, echo = FALSE, fig.height = 5}
missing_stat <- listings_missing_data %>%
  gather(key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  group_by(key) %>%
  mutate(total = n()) %>%
  group_by(key, total, isna) %>%
  summarise(num.isna = n()) %>%
  mutate(pct = num.isna / total * 100)

levels <-
  (missing_stat  %>% filter(isna == T) %>% arrange(desc(pct)))$key

percentage.plot <- missing_stat %>%
  ggplot() +
  geom_bar(aes(
    x = reorder(key, desc(pct)),
    y = pct,
    fill = isna
  ),
  stat = 'identity',
  alpha = 0.8) +
  scale_x_discrete(limits = levels) +
  scale_fill_manual(
    name = "",
    values = c('steelblue', 'tomato3'),
    labels = c("Present", "Missing")
  ) +
  coord_flip() +
  labs(title = "Percentage of missing values", x =
         'Variable', y = "% of missing values")

percentage.plot
```

For the above graphs, I've used ggplot2 library to generate a flipped bar graph to identify the percentage of missing values in the Airbnb dataset. We can identify that the columns neighbourhood_group_cleansed, calendar_updated and bathrooms are empty. Similarly, neighbourhood, overview and host_about has large portions of missing values as well.

```{r fig.align="center", echo = FALSE,fig.width = 12}
top_hosts <- listings %>%
  select(host_id, host_name) %>%
  mutate(name = paste0(host_name, "\n", "(", host_id, ")")) %>%
  count(name, sort = TRUE, name = "count") %>%
  slice(1:10)

ggplot(top_hosts, aes(x=reorder(as.factor(name), -count), y=count)) + 
  geom_bar(stat = "identity", width = 0.5) +
  xlab("Host Name") +
  ylab("Listings")
```
Similarly, the bar chart shows the top hosts in Chicago city. We can observe that host with name Rob and id 3965428 has the most number of listings of property.

```{r fig.align="center", echo = FALSE, fig.height = 10}
# Compare neighbourhood and prices
neighbourhood_price <- listings %>%
  select(neighbourhood, price) %>%
  mutate(price = log1p(as.numeric(price)))

neighbourhood_price %>% 
  ggplot(aes(x=neighbourhood, y=price, fill=neighbourhood)) +
  geom_boxplot(show.legend = FALSE) + coord_flip() 
```

I've also created a box plot chart that provides insights on the neighborhood and prices.