---
title: "Packages"
author:
  - name: Sajal Shrestha 
    url: https://sajalshres.github.io
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Packages are the awesome way of sharing and dsitributing R code that help us to extend the capabilities of R programs and collaborate with others. Throughout my journey to learn R, I've extensively used packages like `dplyr`, `tibble`, `ggplot2`, `boot` etc. I cannot imagine developing R code without support for packages as it made my life much easier and saved a lot of time. So, I wanted to create a custom package to learn how to create packages and install them.

I created a package SearchGithubRepository using the code from functions artifacts. 

The Github link to package is: [https://github.com/sajalshres/SearchGithubRespositories](https://github.com/sajalshres/SearchGithubRespositories) 

## Load Libraries

I've installed and used `devtools` library to install custom package as it is not published yet.

```{r load-packages}
library(devtools)
```

## Load my custom package

I've used `install_github` function to install the  `SearchGithubRespositories` package.

```{r load-custom-package}
install_github("sajalshres/SearchGithubRespositories")
```

## Sample usage

Below is the demonstration of the usage of the package:

```{r custom-package-usage}

SearchGithubRespositories::version()

```

```{r custom-package-usage-2}

response <- SearchGithubRespositories::search_github_repositories(query = "sta-518")
response$total_count

```



